Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Formatting

\noindent
Finally we have the optimisation criteria (criteria 10) to minimise the number of boat changes. This is presented in (\ref{eq22}) and (\ref{eq23}) below.

>>>>

Finally we have the optimisation criteria (criteria 10) to minimise the number
of boat changes. This is presented in \ref{eq22} and \ref{eq23} below.
